```{r}
#| label: variables

Npart = "**40?**"
Nexcl_native = "**NULL**"
Ntrial = 4
Ncond = 8
font = "**24?**-point case Helvetica"
t_blank = 200
t_trial = 25
t_exp = "25 minutes"
ch_limit = 15
paid = "**5?**"
```
# Experiment

Given previous discussion about @LauLiao2018
and following work,\footnote{mainly discuss how syntactic structure might not be the main thing.}
the semantic contribution of the items is need to be discussed.
Even though there are multitude of theoretical discussions on the nature of bare plurals in English,
there is no clear agreement on the nature of their mental or behavioral representations.

The present study tested
people's a priori tendency to complete sentence fragments that starts with bare plurals
in an experimental environment where there is no preceding context.
In addition to their base tendency, the present study aimed to test
how adjectival modification, coordination, or definite marking affects their base tendency.

To this end, we use a sentence completion task with no forced choice.
Participants are asked to provide an appropriate following to sentence fragments
that consist of bare plurals, definite plurals, their modified and/or coordinated forms,
as well as various different structures as fillers,
such as wh-phrases, if clauses, proper names, and adjuncts.

## Methods

The experiment consisted of two parts,
the first part is the preamble completion part.
Participants were provided a sentence fragment and
were asked to provide an appropriate completion.
In the second part of the experiment,
participants were asked to judge sentences using a Likert scale(1-5).
The main rationale behind including a judgment task
was to make participants be more aware of their completions.

### Materials

```{r}
#| label: materials-prep

library(glossr)
use_glossr()
clean_ex <- function(data, explabel) {
    # Filter the data based on the specified column and value
    filtered_data <- data[data[["label"]] == explabel, ]

    # Find columns with value 0 and deselect them
    zero_cols <- which(filtered_data == 0, arr.ind = TRUE)[, 2]
    deselected_data <- filtered_data[, -zero_cols]

    return(deselected_data)
}

examples <- read.csv("./examples.csv")
```

#### Completion Task

The first part of the experiment compromised 2 x 2 x 2 design
(structure: coordination/list x determiner: bare/definite x modification: modified/not-modified).
In total, `r Ntrial` trials were presented in each of the `r Ncond` conditions.
Half of the trials contained two noun phrases both of which sharing the same structure.
The other half of the experimental trials contained a single noun phrase.
All experimental items consisted plural nouns.
Example experimental item (\ref{exp-item}) shows the modified coordinated definite plural condition,
and @tbl-conds shows all manipulations.

```{r}
#| label: exp-item

gloss_df(clean_ex(examples, "exp-item"))
```



| Condition                                 | Example                                  |
| ----------------------------------------- | ---------------------------------------- |
| Bare Plural                               | Mirrors                                  |
| Modified Bare Plural                      | Steamy mirrors                           |
| Coordinated Bare Plurals                  | Mirrors and journeys                     |
| Modified and Coordinated Bare Plurals     | Steamy mirrors and blissful journeys     |
| Definite Plural                           | The mirrors                              |
| Definite Modified Plural                  | The steamy mirrors                       |
| Coordinated Definite Plurals              | The mirrors and journeys                 |
| Modified and Coordinated Definite Plurals | The steamy mirrors and blissful journeys |

: All experimental conditions. {#tbl-conds}


Noun phrases and adjectives were selected from the original study by @LauLiao2018.
Noun phrases were selected randomly,
and the same adjectives from the original study was used for those noun phrases.
Similarly, the coordinands were also kept constant between this study and the original study by @LauLiao2018.

Items were randomly paired into 8 different lists
according to a balanced Latin-square design [@Bradley1958].
Balanced Latin-square made sure that
each item would appear in either one of the condition and
not any other for a participant.
It also removes the immediate carry-over effects:
A condition will precede another condition exactly once.

To preclude participants from limiting themselves to a small set of context,
we included 64 filler sentences.
Fillers consisted of structures that are different from the experimental items.
They can be categorized into 9 different groups as shown in @tbl-fillers.


| Filler Type             | Example                                                  |       Count |
| ----------------------- | -------------------------------------------------------- | ----------: |
| Relative Clause         | The book that kept me up all night                       |          10 |
| Proper Names            | The dynamic duo of Lucy and Max                          |          10 |
| Adjuncts                | During a starry summer night                             |          10 |
| Wh-phrases              | What to do after                                         |          10 |
| Quantified NPs          | Most challenges                                          |           5 |
| Modified Quantified NPs | Few precious chances, which had eluded them for so long, |           5 |
| Conditionals            | If the world was ruled by cats,                          |           6 |
| Inverted Conditionals   | Were I to open a bakery shop,                            |           4 |
| Correlatives            | Wherever the party was                                   |           4 |
|                         |                                                          | *Total*: 64 |

: All filler types, examples, and counts. {#tbl-fillers}

- write how many plurals heads or singular heads participants are seeing in total.

#### Judgment Task

- write about the materials of the second part.

### Procedure

#### Completion Task

The experiment was run online in PCIbex platform [@Drummond2013;@ZehrSchwarz2018].
Each participant session took approximately `r t_exp`.
Participants provided demographic information and
gave informed consent to participate in the experiment.
A practice and instrucstions sessions preceded the experiment,
in which participants were provided with a set of sentence fragments.
Instruction sections included two trials with bare plural noun phrases as sentence fragments,
after they were probed to complete them,
they were also provided other possible completions
which featured both existential and generic examples.
In this section, they were told to not repeat themselves while completing sentences and
provide vivid completions.
They were also instructed about the character (`r ch_limit`) and time limit (`r t_trial` seconds).

Each trial began with `r t_blank` ms blank screen,
and followed by a full sentencen presentation in the center of the screen
that stayed in the screen for `r t_trial` seconds.
In this time period, they were expected to write the sentence completiong and
press \texttt{\textsc{enter}} key.
During the practice item,
a warning message in red font appeared if they did not respond within `r t_trial` seconds or
write more than `r ch_limit` characters, including whitespaces.
Sentence fragments and instructions were presented in black `r font` font on a white background.

- Unlike @LauLiao2018, all experimental items were shown in a random order.



#### Judgment Task

The experiment was run online in PCIbex platform [@Drummond2013;@ZehrSchwarz2018].
Each participant session took approximately `r t_exp`.
Participants provided demographic information and
gave informed consent to participate in the experiment.
A practice and instrucstions sessions preceded the experiment,
in which participants were provided with a set of sentence fragments.
Instruction sections included two trials with bare plural noun phrases as sentence fragments,
after they were probed to complete them,
they were also provided other possible completions
which featured both existential and generic examples.
In this section, they were told to not repeat themselves while completing sentences and
provide vivid completions.
They were also instructed about the character (`r ch_limit`) and time limit (`r t_trial` seconds).

Each trial began with `r t_blank` ms blank screen,
and followed by a full sentencen presentation in the center of the screen
that stayed in the screen for `r t_trial` seconds.
In this time period, they were expected to write the sentence completiong and
press \texttt{\textsc{enter}} key.
During the practice item,
a warning message in red font appeared if they did not respond within `r t_trial` seconds or
write more than `r ch_limit` characters, including whitespaces.
Sentence fragments and instructions were presented in black `r font` font on a white background.

### Participants

- A total of `r Npart` participants were recruited through Prolific. They were paid `r paid` US dollars.
- Speakers (`r Nexcl_native`) that were not native English speakers were excluded.
- Written informed consent was obtained from all participants.


# References
$~$
