```{r}
#| label: variables
# general
Npart <- "**40?**"
Nexcl_native <- "**NULL**"
font <- "**24?**-point case Helvetica"
paid <- "**5?**"

# part 1
Ntrial <- 4
Ncond <- 8
Nprac <- "**10?**"
t_blank <- 200
t_trial <- 25
t_exp <- "25 minutes"
ch_limit <- 15

# part 2
Nprac2 <- "**10?**"
t_blank2 <- 200
t_trial2 <- 25
t_exp2 <- "25 minutes"
```

# Experiment

Given previous discussion about @LauLiao2018
and following work,\footnote{mainly discuss how syntactic structure might not be the main thing.}
the semantic contribution of the items is need to be discussed.
Even though there are multitude of theoretical discussions on the nature of bare plurals in English,
there is no clear agreement on the nature of their mental or behavioral representations.

The present study tested
people's a priori tendency to complete sentence fragments that starts with bare plurals
in an experimental environment where there is no preceding context.
In addition to their base tendency, the present study aimed to test
how adjectival modification, coordination, or definite marking affects their base tendency.

To this end, we use a sentence completion task with no forced choice.
Participants are asked to provide an appropriate following to sentence fragments
that consist of bare plurals, definite plurals, their modified and/or coordinated forms,
as well as various different structures as fillers,
such as wh-phrases, if clauses, proper names, and adjuncts.

## Methods

The experiment consisted of two parts,
the first part is the preamble completion part.
Participants were provided a sentence fragment and
were asked to provide an appropriate completion.
In the second part of the experiment,
participants were asked to judge sentences using a Likert scale(1-5).
The main rationale behind including a judgment task
was to make participants be more aware of their completions.

### Materials

```{r}
#| label: materials-prep

library(glossr)
use_glossr()
clean_ex <- function(data, explabel) {
    # Filter the data based on the specified column and value
    filtered_data <- data[data[["label"]] == explabel, ]

    # Find columns with value 0 and deselect them
    zero_cols <- which(filtered_data == 0, arr.ind = TRUE)[, 2]
    deselected_data <- filtered_data[, -zero_cols]

    return(deselected_data)
}

examples <- read.csv("examples.csv")
```

#### Completion Task

The first part of the experiment compromised 2 x 2 x 2 design
(structure: coordination/list x determiner: bare/definite x modification: modified/not-modified).
In total, `r Ntrial` trials were presented in each of the `r Ncond` conditions.
Half of the trials contained two noun phrases both of which sharing the same structure.
The other half of the experimental trials contained a single noun phrase.
All experimental items consisted plural nouns.
Example experimental item (\ref{exp-item}) shows the modified coordinated definite plural condition,
and @tbl-conds shows all manipulations.


```{r}
#| label: exp-item
by_label <- gloss_factory(examples, ignore_columns = c("parsed", "translation", "language", "source"))

by_label("exp-item")
```



| Condition                                 | Example                                  |
| ----------------------------------------- | ---------------------------------------- |
| Bare Plural                               | Mirrors                                  |
| Modified Bare Plural                      | Steamy mirrors                           |
| Coordinated Bare Plurals                  | Mirrors and journeys                     |
| Modified and Coordinated Bare Plurals     | Steamy mirrors and blissful journeys     |
| Definite Plural                           | The mirrors                              |
| Definite Modified Plural                  | The steamy mirrors                       |
| Coordinated Definite Plurals              | The mirrors and journeys                 |
| Modified and Coordinated Definite Plurals | The steamy mirrors and blissful journeys |

: All experimental conditions. {#tbl-conds}


Noun phrases and adjectives were selected from the original study by @LauLiao2018.
Noun phrases were selected randomly,
and the same adjectives from the original study was used for those noun phrases.
Similarly, the coordinands were also kept constant between this study and the original study by @LauLiao2018.

To preclude participants from limiting themselves to a small set of context,
we included 64 filler sentences.
Fillers consisted of structures that are different from the experimental items.
They can be categorized into 9 different groups as shown in @tbl-fillers.

<!-- TODO write how many plurals heads or singular heads participants are seeing in total. -->

| Filler Type             | Example                                                  |       Count |
| ----------------------- | -------------------------------------------------------- | ----------: |
| Relative Clause         | The book that kept me up all night                       |          10 |
| Proper Names            | The dynamic duo of Lucy and Max                          |          10 |
| Adjuncts                | During a starry summer night                             |          10 |
| Wh-phrases              | What to do after                                         |          10 |
| Quantified NPs          | Most challenges                                          |           5 |
| Modified Quantified NPs | Few precious chances, which had eluded them for so long, |           5 |
| Conditionals            | If the world was ruled by cats,                          |           6 |
| Inverted Conditionals   | Were I to open a bakery shop,                            |           4 |
| Correlatives            | Wherever the party was                                   |           4 |
|                         |                                                          | *Total*: 64 |

: All filler types, examples, and counts. {#tbl-fillers}

#### Judgment Task

The second part of the experiment consisted two types of sentences:
(i) completed versions of the sentences in the first part and
(ii) sentences from @FrazierEtAl2007 study.
Sentences from the first part of the experiment was acquired through a pilot study
carried out voluntarily by University of Maryland graduate students.
We selected 30 sentences from these sentences, covering all experimental conditions and filler types.
From @FrazierEtAl2007 study, we included 20 items using only two conditions from the experiment,
which used bare plurals in the subject positions.
We manipulated whether the first sentence is an episodic (\ref{f-item-a}) or a generic sentence (\ref{f-item-c}).


```{r}
#| label: Frazier-item

gloss_list(by_label("f-item-a", "f-item-c"))
```


### Procedure

#### Completion Task

The experiment was run online in PCIbex platform [@Drummond2013;@ZehrSchwarz2018].
Each participant session took approximately `r t_exp`.
Participants provided demographic information and
gave informed consent to participate in the experiment.
A practice and instrucstions sessions preceded the experiment,
<!-- TODO How many practice items? -->
in which participants were provided with a set of sentence fragments.
Instruction sections included two trials with bare plural noun phrases as sentence fragments,
after they were probed to complete them,
they were also provided other possible completions
which featured both existential and generic examples.
In this section, they were told to not repeat themselves while completing sentences and
provide vivid completions.
They were also instructed about the character (`r ch_limit`) and time limit (`r t_trial` seconds).
In the practice section, they were asked to complete `r Nprac` sentence fragments.

Each trial began with `r t_blank` ms blank screen,
and followed by a full sentence presentation in the center of the screen
that stayed in the screen for `r t_trial` seconds.
In this time period, they were expected to write the sentence completiong and
press \texttt{\textsc{enter}} key.
During the practice item,
a warning message in red font appeared if they did not respond within `r t_trial` seconds or
write more than `r ch_limit` characters, including whitespaces.
Sentence fragments and instructions were presented in black `r font` font on a white background.

Items were randomly paired into 8 different lists
according to a balanced Latin-square design [@Bradley1958].
Balanced Latin-square made sure that
each item would appear in either one of the condition and
not any other for a participant.
It also removes the immediate carry-over effects:
A condition will precede another condition exactly once.
The items in these lists were shuffled as well.

#### Judgment Task

The experiment was run online in PCIbex platform [@Drummond2013;@ZehrSchwarz2018].
Each participant session took approximately `r t_exp2`.
Participants were directed from the previous task,
and greeted by a welcome screen.
Following the initial screen, the instruction and the practice screen were presented,
in which participants judge `r Nprac2` sentences.
In the instructions screen,
participants were told to judge sentences as fast and accurately as possible.
They were also instructed about time limit (`r t_trial2` seconds).

Each trial began with `r t_blank2` ms blank screen,
and followed by a full sentencen presentation in the center of the screen
that stayed in the screen for `r t_trial2` seconds.
In this time period, they were expected to read the sentence and
judge it using the Likert scale presented in the screen.
During the practice item,
a warning message in red font appeared if they did not respond within `r t_trial` seconds.
Sentences and instructions were presented in black `r font` font on a white background.

### Participants

- A total of `r Npart` participants will be recruited through Prolific. They will be paid `r paid` US dollars.
- Written informed consent was obtained from all participants.

#### Exclusion Criteria

- Speakers that were not native English speakers were excluded.
- Participants that failed to XXX task will be exclude, since they will be treated as bots.
- Participants that complete sentence in an inappropriate or repeating way will be excluded.
- Such as completions in the same manner all the time or completions as random strings.



:::{.callout-important}
## To-dos

experiment:

- include "you will not have any money if you do this and this."
- include zach's task or counting task.
- maybe include in the instructions that there are some special tasks
- when a task start with "!!!" give only the correct answer.

completion materials:

- how many plural and singular heads do participants see?

completion procedure: how many practice items

:::


# References
$~$
